Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-18 paper/paper.tex
fix table

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lrrp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Rules created} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & - & - \\
    SYN Flood & - & - \\
    JBoss JMX & 283 & 19 \\
    WeBid & - & - \\    
    ColdFusion & 566 & 37 \\
    .htaccess access & 572 & 1 \\
    .idq access & 700 & 136 \\
    iisadmin access & 502 & 117 \\
    /system32/ in URI & 1,060 & 191 \\
    Script tag in URI & 1,332 & 304 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lrrp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Rules created} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & - & - \\
    SYN Flood & - & - \\
    JBoss JMX & 283 & 219 \\
    WeBid & - & - \\    
    ColdFusion & 566 & 11 \\
    .htaccess access & 572 & 223 \\
    .idq access & 700 & 235 \\
    iisadmin access & 502 & 133 \\
    /system32/ in URI & 1,060 & 368 \\
    Script tag in URI & 1,332 & 287 \\
    \bottomrule
  \end{tabular}
\end{table}
